### 2010-07-01 trunk/paper/IIWAS2010/content/system_arch.tex
latest version

% Algorithm 1: figure  
\begin{figure}[t]
	\centering
%\includegraphics[width=85mm]{../img/vehicular_ontology.eps}
\includegraphics[width=85mm]{vehicular_ontology.eps}
\caption{Abbreviated Vehicular Ontology}% - arrows represent inheritance relationships between the ontological classes.}
\label{fig:vehicular_ontology}
\end{figure}

Suppose we want to find the category divergence between \textit{Sedan} and \textit{Bus} Figure \ref{fig:vehicular_ontology}. \textit{Sedan} is the subcategory of \textit{Sedan}, and \textit{Bus} is the subcategory of \textit{Automobile}. Therefore, the least common ancestor ($C$) for these two. This section presents ontology and copora, query processing, ranking queries, and the query resolution mechanism. categories is \textit{Automobile}. In addition, the tree height \textit{h = 4}. So, the normalized divergence $cd$\textit{(Sedan, Bus)} is \textit{7/12} that is calculated from \textit{d(Sedan, Root) = 4}, \textit{d(Sedan, Automobile) = 2}, and \textit{d(Bus, Automobile) = 1}.

>>>>

% Algorithm 1: figure  
%\begin{figure}[t]
%	\centering
%\includegraphics[width=85mm]{../img/vehicular_ontology.eps}
%\includegraphics[width=85mm]{vehicular_ontology.eps}
%\includegraphics[width=85mm]{img/OntologyDiagram.eps}
%\caption{Abbreviated Vehicular Ontology}% - arrows represent inheritance relationships between the ontological classes.}
%\label{fig:vehicular_ontology}
%\end{figure}

\begin{figure}[t]
	\includegraphics[scale=.65]{../img/OntologyDiagram.png}
	\caption{Abbreviated Vehicular Ontology}
	\label{fig:vehicular_ontology}
\end{figure}

Suppose we want to find the category divergence between \textit{Sedan} and \textit{Bus} Figure \ref{fig:vehicular_ontology}. \textit{Sedan} is the subcategory of \textit{Sedan}, and \textit{Bus} is the subcategory of \textit{Automobile}. Therefore, the least common ancestor ($C$) for these two. This section presents ontology and copora, query processing, ranking queries, and the query resolution mechanism. categories is \textit{Automobile}. In addition, the tree height \textit{h = 4}. So, the normalized divergence $cd$\textit{(Sedan, Bus)} is \textit{7/12} that is calculated from \textit{d(Sedan, Root) = 4}, \textit{d(Sedan, Automobile) = 2}, and \textit{d (Bus, Automobile)=1}.
